Provisional Title

### 2021-05-01 draft/draft.tex
final fig1, initializing fig2, samll changes to methods

Beta-diversity indexes between the invasive and coalesced communities
or the resident and coalesced communities were performed using Bray–Curtis or
Jensen-Shannon similarity metrics. For two abrbitrary communities with
ESV abundances represented by the vectors
$\mathbf{x} = \left( x_1, x_2, \cdots, x_N \right)$
and
$\mathbf{y} = \left( y_1, y_2, \cdots, y_N \right)$
(where $x_i$ and $y_i$ represent the relative abundance of the $i$th ESV in
each community respectively and $N$ is the total number of ESVs), the Bray-Curtis
similarity $\mathrm{BC} \left( \mathbf{x}, \mathbf{y} \right)$ is calculated as
\cite{Bray1957}

\begin{equation}
\mathrm{BC} \left( \mathbf{x}, \mathbf{y} \right) = 
\sum_i \mathrm{min} \left( x_i , y_i \right)
\label{eq:bray-curtis}
\end{equation}
%
and the Jensen-Shannon similarity
$\mathrm{JS} \left( \mathbf{x}, \mathbf{y} \right)$
is defined as one minus the Jensen-Shannon distance (which is, in turn,
the square root of the Jensen-Shannon divergence \cite{Lin1991})

@@

\begin{equation}
\mathrm{KL} \left( \mathbf{x}, \mathbf{y} \right) = 
\sum_i x_i \; \mathrm{log_2} \left( \frac{x_i}{y_i} \right)
\label{eq:kullback-leibler}
\end{equation}

Additionally, we used alternative metrics that do not account for the specific
fractions of each ESV (that is, only discern whether a ESV is present or absent
in a community). These are the Jaccard similarity
$\mathrm{J} \left( \mathbf{x}, \mathbf{y} \right)$ \cite{Jaccard1912}
and the fraction of the endemic cohort of the invasive community
that persists in the coalesced one,
denoted as
$\mathrm{E} \left( \mathbf{x}_\mathrm{I},
\mathbf{x}_\mathrm{R},
\mathbf{x}_\mathrm{C} \right)$
where the subindices I, R and C correspond to the invasive, resident and coalesced
communities respectively.

\begin{equation}
\mathrm{J} \left( \mathbf{x}, \mathbf{y} \right) = 
\frac{\left|\; \mathbf{x} \cap \mathbf{y} \;\right|}
{\left|\; \mathbf{x} \cup \mathbf{y} \;\right|}
\label{eq:jaccard}
\end{equation}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=12cm,keepaspectratio]{figs/fig1.pdf}
\caption{\textbf{Overview of the experimental protocol.}
\textbf{a.}~Environmental samples obtained from eight different locations were used
to inoculate our communities.
\textbf{b.}~Communities were stabilized in serial batch culture bioreactors
\cite{Goldford2018} in minimal synthetic media with glutamine or citrate as the
only supplied carbon source.
\textbf{c.}~Communities were plated in minimal media agar plates and the most abundant
species (the ``dominants") from each community were isolated. We refer to the set of
sub-dominant species as the ``cohorts".
\textbf{d.}~Rank-frequency distributions of all eight communities stabilized in either
glutamine (red) or citrate (blue), sequenced at a depth of $10^{-4}$ reads.
Three biological replicates per community are shown.
Community compositions are skewed and long-tailed.
\textbf{e.}~Our hypothesis is that ecological co-selection can take place from the top-down,
i.e. the dominant co-selecting the cohort, or from the bottom-up, i.e. the cohort co-selecting
the dominant. Both forms of co-selection can be positive (recruitment) or negative
(antagonism).
\textbf{f.}~Illustration of the protocol of our coalescence experiments.}
\label{fig1}
\end{figure}

>>>>

Beta-diversity indexes between the invasive and coalesced communities
or the resident and coalesced communities were computed using various
similarity metrics. For two arbitrary communities with
ESV abundances represented by the vectors
$\mathbf{x} = \left( x_1, x_2, \cdots, x_N \right)$
and
$\mathbf{y} = \left( y_1, y_2, \cdots, y_N \right)$
(where $x_i$ and $y_i$ represent the relative abundance of the $i$th ESV in
each community respectively and $N$ is the total number of ESVs), the Bray-Curtis
similarity $\mathrm{BC} \left( \mathbf{x}, \mathbf{y} \right)$ is calculated as
\cite{Bray1957}

\begin{equation}
\mathrm{BC} \left( \mathbf{x}, \mathbf{y} \right) = 
\sum_i \mathrm{min} \left( x_i , y_i \right)
\label{eq:bray-curtis}
\end{equation}
%
The Jensen-Shannon similarity
$\mathrm{JS} \left( \mathbf{x}, \mathbf{y} \right)$
is defined as one minus the Jensen-Shannon distance (which is, in turn,
the square root of the Jensen-Shannon divergence \cite{Lin1991})

@@

\begin{equation}
\mathrm{KL} \left( \mathbf{x}, \mathbf{y} \right) = 
\sum_i x_i \; \mathrm{log_2} \left( \frac{x_i}{y_i} \right)
\label{eq:kullback-leibler}
\end{equation}
%
The Jaccard similarity is given by
$\mathrm{J} \left( \mathbf{x}, \mathbf{y} \right)$ \cite{Jaccard1912}

\begin{equation}
\mathrm{J} \left( \mathbf{x}, \mathbf{y} \right) = 
\frac{\left|\; \mathbf{x} \cap \mathbf{y} \;\right|}
{\left|\; \mathbf{x} \cup \mathbf{y} \;\right|}
\label{eq:jaccard}
\end{equation}
%
For all the metrics above, we quantify the relative similarity between the invasive
and the coalesced communities using relative metrics (Q):

\begin{equation}
\mathrm{Q} \left( \mathbf{x}_\mathrm{I},
\mathbf{x}_\mathrm{R},
\mathbf{x}_\mathrm{C} \right) = 
\frac{\mathrm{F} \left( \mathbf{x}_\mathrm{I},\mathbf{x}_\mathrm{C}\right)}
{\mathrm{F} \left( \mathbf{x}_\mathrm{I},\mathbf{x}_\mathrm{C}\right)
+
\mathrm{F} \left( \mathbf{x}_\mathrm{R},\mathbf{x}_\mathrm{C}\right)}
\label{eq:q}
\end{equation}
%
where the subindices I, R and C correspond to the invasive, resident and coalesced
communities respectively, and F represents one of BC (Bray-Curtis similarity), JS
(Jensen-Shannon similarity) or J (Jaccard similarity) defined in equations
\ref{eq:bray-curtis} to \ref{eq:jaccard}.

Additionally, we quantify coalescence outcomes by examining the fraction of the endemic
cohort of the invasive community that persists in the coalesced one. We denote this
metric as
$\mathrm{E} \left( \mathbf{x}_\mathrm{I},
\mathbf{x}_\mathrm{R},
\mathbf{x}_\mathrm{C} \right)$.

@@

\begin{figure}[!h]
\centering
\includegraphics[width=12cm,keepaspectratio]{figs/fig1.pdf}
\caption{\textbf{Overview of the experimental protocol.}
\textbf{a.}~Environmental samples collected from eight different locations were used
to inoculate our communities.
\textbf{b.}~Communities were stabilized in serial batch culture bioreactors
\cite{Goldford2018} in minimal synthetic media with glutamine or citrate as the
only supplied carbon source.
\textbf{c.}~Communities were plated in minimal media agar plates and the most abundant
species (the ``dominants") from each community were isolated. We refer to the set of
sub-dominant species as the ``cohorts".
\textbf{d.}~Rank-frequency distributions of all eight communities stabilized in either
glutamine (red) or citrate (blue), sequenced at a depth of $10^{-4}$ reads.
Three biological replicates per community are shown.
Community compositions are skewed and long-tailed.
\textbf{e.}~Our hypothesis is that ecological co-selection can take place from the top-down,
i.e. the dominant co-selecting the cohort, or from the bottom-up, i.e. the cohort co-selecting
the dominant. Both forms of co-selection can be positive (recruitment) or negative
(antagonism).
\textbf{f.}~Illustration of the protocol of our coalescence experiments. All pairs of
communities were inoculated into fresh minimal media supplemented with the same carbon
source where communities had been previously stabilized. The coalesced (C) and original
resident (R) and invasive (I) communities were then serially diluted and allowed to grow
for seven additional transfers.}
\label{fig1}
\end{figure}
